\documentclass[../../main.tex]{subfiles}
\graphicspath{{../}}

\begin{document}

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
While doing this thesis, I have received a great deal of support and assistance. I would first like to thank my thesis supervisor Professor Filippo Sanfilippo of the Faculty of Technology, Natural Sciences and Maritime Sciences at the University of South-Eastern Norway. His invaluable guidance and support helped me in all the time of research and writing of this thesis.

In addition, I would like to express my very great gratitude to the University of South-Eastern Norway (USN) for supporting me in one year exchange regarding the NORPART scholarship. Thanks to the scholarship, I have a chance to participate in the Master of Science in Systems Engineering with Embedded Systems. After one year in Norway, I have learned not only technical knowledge but also Norwegian culture.

I would like to express my very great appreciation to professors and lecturers, especially professor Huynh Thai Hoang and professor Nguyen Vinh Hao, in the Department of Control Engineering and Automation, Faculty of Electrical and Electronics Engineering at the Ho Chi Minh University of Technology. Thanks to their enthusiastic instruction, I gained a solid background in control theory and electronics techniques.

Besides my supervisor, I would also like to thank my colleagues: Steven Bos, Erlend Helgerud and Thong Ho for their wonderful collaboration. It is my honour to have an opportunity to work with them. With their enthusiastic help, I have had a chance to broaden my knowledge.

Last but not least, I must express my very deep gratitude to my parents for giving me continuous encouragement through the process of researching and writing this thesis. Their love helps me to overcome the difficulties to achieve accomplishments in my life.

\end{document}